Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2014-12-20 Paper/paper.tex
plates
Add stuff from presentation to paper.

\documentclass[11pt,twocolumn]{scrartcl}

@@

@@

\section{Induction Models}
\subsection{Model 0}
\subsection{Model 1}

\section{Data}
\subsection{Google Syntactic-ngrams}
Here we talk a bit about the syntactic n-grams and all that \cite{ngrams2013}.
\subsection{Pruning}

@@

\section{Results}

>>>>

\documentclass[10pt,twocolumn]{scrartcl}

\usepackage{amsmath}

@@

\usepackage{tikz}
\usetikzlibrary{bayesnet}

@@

\section{Induction Models}

\subsection{Model 0: Un-structured Tuples}
\begin{tabbing}
    $N$ \hspace{10pt}\= number of data points\\
    $F$              \> number of frames\\
    $\theta$         \> distribution over frames\\
    $\varphi_a$      \> distributions (for each frame) over \\ 
                     \> vocabulary of argument $a$\\
    $w_a$            \> datapoint (verb, subject, object)\\
\end{tabbing}
E-Step:
\begin{equation}
P(f|w_i) = \frac{\prod_a^{\{v,s,o\}}P(w_i^a|\phi_f^a) P(f|\theta)}{\sum_{f'}^F\prod_a^{\{v,s,o\}}P(w_i^a|\phi_{f'}^a)}
\end{equation}
M-Step:
\begin{equation}
P(f|\theta) = \frac{\sum_{i=1}^N \mu_i(f)}{\sum_{f'=1}^F\sum_{i=1}^N\mu_i(f')}
\end{equation}
\begin{equation}
P(w|\phi_f^a) = \frac{\sum_{i=1}^N \mu_i(f) C(w,a)}{\sum_{w'=1}^{V^a}\sum_{i=1}^N \mu_i(f) C(w',a)}
\end{equation}
\begin{tabbing}
    $n$ \hspace{10pt}\= number of data points\\
    $f$              \> number of frames\\
    $v$              \> number of documents (= verb vocabulary)\\
    $\theta$         \> distribution over frames\\
    $\varphi_a$      \> distributions (for each frame) over \\ 
                     \> vocabulary of argument $a$\\
    $w_a$            \> datapoint (verb, subject, object)\\
    $\beta$          \> hyperprior for $\varphi$ (for each argument)\\
    $\alpha$         \> hyperprior for $\theta$ \\
\end{tabbing}

\begin{figure}
\input{model0plate.tex}
\caption{Model 0}
\end{figure}

\subsection{Model 1: Verb Documents}
Gibbs:
\begin{align}
&p(z_{ij} = f| \mathbf{f}_{-ij},\alpha,\beta,\mathbf{w})\\
\propto &\prod_a^{\{v,s,o\}}\frac{\beta^a + \tilde{c}(f,w_{ij})}{V^a + \tilde{c}(f)}
        \cdot \frac{\alpha + \tilde{c}(i,f)}{f\alpha+\tilde{c}(i)}
\end{align}

\begin{tabbing}
    $\tilde{c}(f,w_{ij})$ \hspace{10pt}\= times $w_{ij}$ is assigned to frame $f$\\
    $\tilde{c}(f)$                     \> total data points assigend to $f$\\
    $\tilde{c}(i,f)$                   \> VSOs in document $i$ assigned to $f$\\
    $\tilde{c}(i)$                     \> VSOs in document $i$\\ 
\end{tabbing}

\begin{figure}
    \input{model1plate.tex}
    \caption{Model 1}
\end{figure}

\section{Data}

\subsection{Google Syntactic-ngrams}
Here we talk a bit about the syntactic n-grams and all that \cite{ngrams2013}.
\begin{itemize}
    \item A syntactic-ngram is a $k$-word rooted subtree for some sentence. 
    \item Google ngrams come from a corpus of 3.5 million English books.
    \item We trimmed the ``verb args'' dataset to consider only subject-verb-object triples (VSO's).
    \item The dataset contains 1,629,120 unique VSO's with a total of 96,245,401 by count.
    \item In our final results we may only use the most common \%20 of these...
\end{itemize}

\subsection{Pruning}

@@

\section{Results}
\subsection{Frame Coherency}
rame coherency: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random choses verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$  
\subsection{Frame Correctness}
Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
\subsection{Model 0}
\subsection{Model 1}
